Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/30-dataset.tex
shorter captions for figs 6 and 7

\textbf{OCR Q.A.}  The predicted text by the OCR system is aligned with the groundtruth text using standard tools from
Stephen V. Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at
the entry level and at the global level defined as the ratio between the number of errors
(insertions/deletions/substitutions) over the reference text length.

>>>>

\textbf{OCR Q.A.}  The predicted text by the OCR system is aligned with the groundtruth text using standard tools from
Stephen V. Rice's thesis~\cite{santos.2019.wcmel,neudecker.2021.whdip}. The Character Error Rate (CER) is computed at
the entry level and at the global level, defined as the ratio between the number of errors
(insertions/deletions/substitutions) over the reference text length.

### 2022-01-20 src-latex/parts/50-ner-xp1-training-set-size-and-pretraining.tex
shorter captions for figs 6 and 7

% !TeX root = ../main-paper.tex
\section{Experiment 1: NER sensibility to the number of training examples}
\label{sec:ner-xp1}
The constitution of annotated example sets to train a NER model on a target domain is a critical preliminary step.
Often done manually, possibly from bootstrapped annotations, this task is tedious, time-consuming and error-prone.
The ability of a model to perform well even with few training examples is a practical criteria to consider.
In this first experiment, we investigate the NER performance of SpaCy and CamemBERT when fine-tuned with an increasing number of training examples.

@@

%First, we split the ground truth into a training set, a development set, and a test set. 
%The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.
As the organisation and structure of entries varies across directories, the models may learn to overfit on a subset of directories with specific features. 
To reduce the evaluation bias, we start by leaving out 3 directories (1690 entries, $\approx 19\%$) from the ground truth as a test set containing entries from unseen directories.

@@

To generate smaller training sets, we start from the initial training set and iteratively split it in half using the same stratified sampling strategy as for the train/dev split to maintain the relative frequency of directories. 
We stop if a directory has only one entry left, or if the current training subset contains less than 30 entries maintaining the relative frequency of directories within it
Applying this procedure to the initial training set produced 8 training subsets containing 49, 99, 199, 398, 796, 1593, 3186, and 6373 entries.

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes. As SpaCy NER is outperformed by both BERT models from the start, CmBERT slightly surpasses the pre-trained version when the number of training examples becomes large. Values for precision and recall are available in the appendix.\bertrand{TODO!}}
\end{figure}

>>>>

% !TeX root = ../main-paper.tex
\section{Experiment 1: NER sensibility to the number of training examples}
\label{sec:ner-xp1}
The constitution of annotated datasets to train a NER model is a critical preliminary step.
Often done manually, possibly with bootstrapped annotations, this task is tedious, time-consuming, and error-prone.
The ability of a model to perform well even with a few training examples is a practical criterion to consider.
In this first experiment, we investigate the NER performance of SpaCy and CamemBERT when fine-tuned with an increasing number of training examples.

@@

%First, we split the ground truth into a training set, a development set, and a test set. 
%The training set is then gradually reduced in size while maintaining the relative frequency of directories within it.
As the structure of entries varies across directories, the models may learn to overfit on a subset of directories with specific features. 
To reduce the evaluation bias, we start by leaving out 3 directories (1690 entries, $\approx 19\%$) from the ground truth as a test set containing entries from unseen directories.

@@

To generate smaller training sets, we start from the initial training set and iteratively split it in half using the same stratified sampling strategy as for the train/dev split to maintain the relative frequency of directories. 
We stop if a directory has only one entry left, or if the current training subset contains less than 30 entries, maintaining the relative frequency of directories within it
Applying this procedure to the initial training set produces 8 training subsets containing 49, 99, 199, 398, 796, 1593, 3186, and 6373 entries.

@@

\begin{figure}[ht!]
	   \center{\includegraphics[width=\textwidth]
	       {figs/eval-ner-exp1.pdf}}
	  \caption{\label{fig:f1-vs-trainsize} Metrics measured on the fine-tuned models CmBERT, CmBERT+ptrn and SpaCy NER in experiment 1 for 8 training sets of increasing sizes. Precision and recall values are available in the appendix.}
\end{figure}

### 2022-01-20 src-latex/parts/60-ner-xp2-pretraining-and-finetuning.tex
Updates from Overleaf
shorter captions for figs 6 and 7

CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
Finally the metrics are measured against the three tests sets.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores (in \%) of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).  Results show that best performances on noisy entries are obtained when the model has been pre-trained and fine-tuned for NER on examples affected with a similar OCR noise.}
\end{figure}

>>>>

CmBERT and CmBERT+ptrn are fine-tuned on the training sets built from NER-\emph{reference} and NER-\emph{pero}.
The training parameters are mostly the same as in \cref{sec:ner-xp1-protocol}, only this time the patience threshold is set to 5 evaluations.
Finally the metrics are measured against the three tests sets.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.75\textwidth]{images/experiment_2_f1_with_noise_graph.pdf}
    \caption{\label{fig:exp_2_eval_ner}F1 scores of NER predictions in presence of OCR noise in the training and testing examples, grouped by test set. The dataset used to train the NER task is noted in indice after the model name (e.g. CmBERT$_{pero}$ means CmBERT fine-tuned on NER-\emph{pero}).}
\end{figure}
